Staged Abstract Interpreters

### 2019-04-06 paper/70_eval.tex
eval

Figure~\ref{evaluation_result} shows the evaluation result, comparing the
performance improved by staging on 0CFA without and with store-widening. The
\textit{unstaged} and \textit{staged} columns show the median time to finish the
analysis. The column $\frac{\text{unstaged}}{\text{staged}}$
shows the improvement from staging. The dash - in some cells indicates timeout.
As we can see from the table, the staged version significantly outperforms the
unstaged version on all benchmarks, especially for the @kcfa-worst-@$n$ series.
We observe the most improvement of 29x times faster than the unstaged version on
@solovay-strassen@. On average, the staging produces code that runs 11x times faster
than the unstaged analyzer.

>>>>

Figure~\ref{evaluation_result} shows the evaluation result, comparing the
performance improved by staging on two monovariant CFA (without and with store-widening). The
\textit{unstaged} and \textit{staged} columns show the median time to finish the
analysis. The column $\frac{\text{unstaged}}{\text{staged}}$
shows the improvement from staging. The dash - in some cells indicates timeout.
As we can see from the table, the staged version significantly outperforms the
unstaged version on all benchmarks. %, especially for the @kcfa-worst-@$n$ series.
We observe the most improvement of 29x times faster than the unstaged version on
@solovay-strassen@. On average, the staging produces code that runs 11x times faster
than the unstaged analyzer.
